\LARGE Performance Evaluation of Xenomai 3

### 2015-10-21 paper.tex
mention Copperplate and avoid API level benchmarking

@@

\section{Conclusions}
The trait of real time in RTLinux is closely related to hardware, So we can take full advantage of PC. The testing on our recorder showed that the average of interrupt response time is 10us, and the max  is 15us. This performance can satisfy this real time requirement of recorder completely and guarantee data integrity. With the high-performance and  great capacity hard disk using, the capacity of the RAID would reach over 1000GB, moreover, collected data don't loss even if one hard disk is demaged.

We had done the test that  under the same hard platform, the recording speed has significantly enhanced in RTLinux than in Windows NT. RTLinux is free, open source, retractile, and transferable, so many OS can not bear comparison with it. RTLinux has been applied successful in our pre-demodulation Digital Recorder; moreover, it will be more widely used in the field of real-time control.

>>>>

In Xenomai 3, with the introduction of the \textit{Copperplate} interface, which mediates between the real-time API / emulator of given application uses, and the underlying real-time core. That is, applications are able to run in either environments without visible code change. We do not intend to measure the overhead of \textit{Copperplate} interface or its implementation for the sake of measuring the system-level performance rather than API-oriented emulation.

@@

\section{Conclusions}
